Price of Anarchy for Mean Field Games

### 2018-07-26 PoA.tex
minor change prop 7
added assumptions D_u \neq D_w for Prop 6 Case 1 and Prop 7 Cases 1 and 2

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{RL}
		& C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		\leq & C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
	%	= & C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}}  \\
		\leq &  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} < \infty,
	%	< & \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
	&	D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
	\geq & \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
	%=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
	%	&\geq(-A^u + \left\vert A_u \right\vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
	\geq & -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } >  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{equation*}
			\left\vert u_t^{r} \right\vert  \leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2
	\end{equation*}
%	\begin{IEEEeqnarray*}{rCl}
%		\left\vert u_t^{r} \right\vert  &=& \frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \nonumber \\
%		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2
		% &=:&c_2. 
%	\end{IEEEeqnarray*}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

% proposition b2 bar infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$, then:
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	%First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure. Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	\begin{equation*}
	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.     
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$\\

@@

% proposition b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), $b_1>0$, $\bar{b}_1>0$, the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
	\begin{split}
		\left|u^{b_1}_t\right| &\leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		&\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon}\\
		&=:c,
	\end{split}
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. By our assumption on $\bar{b}_1$, we have $A^{u,b_1\to 0} \neq A^{w,b_1\to 0}$ and thus, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

@@

    Now we consider $b_1 \to \infty$. For each $b_1>0$, we have the following bounds over $t\in[0,T]$:
    \begin{equation*}
    \begin{split}
	    \left| u^{b_1}_t\right| &\leq \frac{C^u+D^u(\delta^{+,b_1}_u-\delta^{-,b_1}_u)}{-\delta^{-,b_1}_u}=:h_u(b_1) \\
		\left| w^{b_1}_t\right| &\leq \frac{C^w+D^w(\delta^{+,b_1}_w-\delta^{-,b_1}_w)}{-\delta^{-,b_1}_w}=:h_w(b_1) \\
		\left| \eta^{b_1}_t\right| &\leq \frac{C^{\eta}+D^{\eta}(\delta^{+,b_1}_{\eta}-\delta^{-,b_1}_{\eta})}{-\delta^{-,b_1}_{\eta}}=:h_{\eta}(b_1) \\
		\left| \bar{x}^{MFG,b_1}_t \right| &\leq \left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)}=:h_{\bar{x}}(b_1).
    \end{split}
    \end{equation*}
    Thus, from Proposition \ref{prop:diff_SC}, we have:
    \begin{equation*}
	    \Delta SC^{b_1} \leq \frac{1}{2}BT(h_u(b_1)+h_w(b_1))^2 (h_{\bar{x}}(b_1))^2.
    \end{equation*}
    We also have the following lower bound:
    \begin{equation*}
	\begin{split}
	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
	& \geq \frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
	\end{split}
    \end{equation*}

@@

    \begin{equation*}
    \begin{split}
	    \frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}&\leq \frac{2BT(h(b_1))^2 (h_{\bar{x}}(b_1))^2}{\frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BT(h(b_1))^2 (\left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)})^2}{(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BTe^{2T(\bar{b}_1)}(\mathbb{E}(\xi))^2  }{(q_T+\bar{q}_T)Var(\xi)} \cdot \frac{(h(b_1))^2}{e^{-2TB^{\eta}h(b_1))}}\\
	    &\xrightarrow[b_1 \to \infty ]{} 0.
    \end{split}
    \end{equation*}
    Therefore,
    \begin{equation*}
	    \lim_{b_1 \to \infty}\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}=0,
    \end{equation*}
    and thus, $\lim_{b_1 \to \infty} PoA^{b_1}=1$. ToDo: last case.

>>>>

	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
	\begin{IEEEeqnarray*}{RL}
		& C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
		\leq & C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
	%	= & C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}}  \\
		\leq &  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} < \infty,
	%	< & \infty,
	\end{IEEEeqnarray*}
	and 
	\begin{IEEEeqnarray*}{rl}
	&	D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
	\geq &  \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}\\
	%\geq & \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
	%=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
	%	&\geq(-A^u + \left\vert A_u \right\vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
	\geq & -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } >  0.
	\end{IEEEeqnarray*}
	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
	\begin{equation*}
			\left\vert u_t^{r} \right\vert  \leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2
	\end{equation*}
%	\begin{IEEEeqnarray*}{rCl}
%		\left\vert u_t^{r} \right\vert  &=& \frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \nonumber \\
%		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2
		% &=:&c_2. 
%	\end{IEEEeqnarray*}
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$

@@

% proposition b2 bar infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$, and:
	\begin{equation*}
		\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}
	\end{equation*}
	then:
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	%First, we consider $\bar{b}_2 \to 0$. For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.

@@

   	By the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u,\bar{b}_2 \to 0} \neq D^{w,\bar{b}_2 \to 0}$, and thus by continuity, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure. Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	\begin{equation*}
	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.     
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$\\

@@

% proposition b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon} := c
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u} \neq D^{w,b_1}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

@@

    \begin{comment}
    Now we consider $b_1 \to \infty$. For each $b_1>0$, we have the following bounds over $t\in[0,T]$:
    \begin{equation*}
    \begin{split}
	    \left| u^{b_1}_t\right| &\leq \frac{C^u+D^u(\delta^{+,b_1}_u-\delta^{-,b_1}_u)}{-\delta^{-,b_1}_u}=:h_u(b_1) \\
		\left| w^{b_1}_t\right| &\leq \frac{C^w+D^w(\delta^{+,b_1}_w-\delta^{-,b_1}_w)}{-\delta^{-,b_1}_w}=:h_w(b_1) \\
		\left| \eta^{b_1}_t\right| &\leq \frac{C^{\eta}+D^{\eta}(\delta^{+,b_1}_{\eta}-\delta^{-,b_1}_{\eta})}{-\delta^{-,b_1}_{\eta}}=:h_{\eta}(b_1) \\
		\left| \bar{x}^{MFG,b_1}_t \right| &\leq \left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)}=:h_{\bar{x}}(b_1).
    \end{split}
    \end{equation*}
    Thus, from Proposition \ref{prop:diff_SC}, we have:
    \begin{equation*}
	    \Delta SC^{b_1} \leq \frac{1}{2}BT(h_u(b_1)+h_w(b_1))^2 (h_{\bar{x}}(b_1))^2.
    \end{equation*}
    We also have the following lower bound:
    \begin{equation*}
	\begin{split}
	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
	& \geq \frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
	\end{split}
    \end{equation*}

@@

    \begin{equation*}
    \begin{split}
	    \frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}&\leq \frac{2BT(h(b_1))^2 (h_{\bar{x}}(b_1))^2}{\frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BT(h(b_1))^2 (\left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)})^2}{(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
	    &= \frac{4BTe^{2T(\bar{b}_1)}(\mathbb{E}(\xi))^2  }{(q_T+\bar{q}_T)Var(\xi)} \cdot \frac{(h(b_1))^2}{e^{-2TB^{\eta}h(b_1))}}\\
	    &\xrightarrow[b_1 \to \infty ]{} 0.
    \end{split}
    \end{equation*}
    Therefore,
    \begin{equation*}
	    \lim_{b_1 \to \infty}\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}=0,
    \end{equation*}
    and thus, $\lim_{b_1 \to \infty} PoA^{b_1}=1$. ToDo: last case.
\end{comment}

	Todo: case $b_1 \to \infty$ and $\bar{b}_1 \to \infty$.
\end{proof}
